Twisted graviton spectra of $AdS_4\times S^7$ and $AdS_7\times S^4$

### 2023-05-30 graviton spectra/content/index.tex
support conditions
e16

%The phase space is equipped with a natural symplectic form given by
%\[
%\int_C \d z \oint_{S^2} \d w \, \alpha \wedge \alpha' .
%\]
%There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bullet}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C - 0$ which extends to zero.
%The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$
\subsection{States on twisted $AdS_4\times S^7$}\label{s:ads4states}
We begin more generally with the input being a three-manifold $M$ equipped with a THF structure of codimension one.
As in \S \ref{s:??} the elliptic complex $\cA^\bu_M$ computes the THF cohomology of $M$.
We denote by $K$ the holomorphic canonical bundle of $M$ which has a local frame given by $\d z$.
The case of $AdS_4 \times S^7$ corresponds to taking $M = \R \times \C$, which we will do momentarily.

We will also fix a fourth-root $K^{1/4}$ of this bundle.
Following the above prescription, we consider the $S^7$ bundle 
\[
\begin{tikzcd}
S^7 \ar[r] & \operatorname{Tot} (K^{1/4} \otimes \C^4 \to M) \setminus 0(M) \ar[d, "p"] \\ & \R_{>0}\times M
\end{tikzcd}
\]
We wish to describe the free limit of the pushforward $p_* \mc E^N_{AdS_4}$ as a sheaf of cochain complexes on $\R_{>0}\times M$.

@@

\parsec{}
We proceed to define a natural boundary condition of the twisted $AdS_4$-type theory at $\{\infty\} \times M \subset \R_{>0} \times M$. 
Such a boundary condition is specified by a Lagrangian in the phase space whose symplectic structure uses Serre duality on the THF manifold $M$ together with the higher residue pairing along the THF structure of the sphere $S^7$. 
The restriction $(p_* \mc E^N_{AdS_4})|_{\{\infty\}\times \C}$ describes the phase space and is easily seen to be $\cA_M^\bu (\mc V^N)$. We wish to describe a shifted Lagrangian therein.

@@

Thus we see that a natural Lagrangian in the phase space is given by the sheaf of cochain complexes $\cA^\bu_M(\mc L^N_{AdS_4})$ where $\mc L^N_{AdS_4}$ is the following complex of vector bundles on $M$:

@@

We now specialize to the case $M = \R \times \C$.

\begin{defn}\label{defn:ads4states}
 The \emph{space of supergravity states} on twisted $AdS_4\times S^7$ is given by the costalk at zero of the factorization algebra on $\R\times \C$ given by 
 \beqn
 \cO\left(\Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C (\mc L^N_{AdS_4}) \right ) .
 \eeqn
\end{defn}

@@

\begin{lem}\label{lem:ads4states}
The space of supergravity states on twisted $AdS_4\times S^7$ is the symmetric algebra $\Sym (\mc H_{AdS_4})$ where $\mc H_{AdS_4}$ is the cochain complex
 \begin{equation} 
 \begin{tikzcd}[row sep = 1 ex]
    \ul{-} & \ul{+} \\ 
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \C[\del_z]\delta_{z=0}\ar[r, "\del^W_\Omega" description] & \C[w_1,\ldots, w_4]  \otimes \C[\del_z]\delta_{z=0} \\
\C[w_1,\ldots, w_4] \del_z  \otimes \C[\del_z]\delta_{z=0}\ar[ur, "\del^M_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \C[\del_z]\delta_{z=0}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \d z \otimes \C[\del_z]\delta_{z=0} \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \C[\del_z]\delta_{z=0}
\end{tikzcd}
\end{equation}
\end{lem}

@@

\begin{prop}
The single particle index of the space of supergravity states $\mc H_{AdS_4}$ is given by 
\[
f_{AdS_4} (t_1, t_2, t_3, q)  = \frac{q\left (\begin{aligned} q^{1/4}(t_1+ t_2 + t_3+t_1^{-1}t_2^{-1}t_3^{-1}) &+ q^{-1} \\- q^{-1/4}(t_1^{-1}+ t_2^{-1} + t_3^{-1}+t_1t_2t_3) &- q   \end{aligned}\right)}{(1-q)(1-q^{1/4}t_1)(1-q^{1/4}t_2)(1-q^{1/4}t_3)(1-q^{1/4}t_1^{-1}t_2^{-1}t_3^{-1})}
\]
\end{prop}
\begin{proof}
The two summands not involving holomorphic vector fields or forms appear with opposite parity, so their contributions to the character cancel. For the remaining summands, It is straightforward to compute the character of each tensor factor:
\begin{itemize}
\item The factor $\C[\del_z]\delta_{z=0}$ contributes a factor of \[\frac{q}{1-q}.\]
\item The tensor factor $\C[w_1,\cdots, w_4]$ contributes a factor of \[\frac{1}{(1-q^{1/4}t_1)(1-q^{1/4}t_2)(1-q^{1/4}t_3)(1-q^{1/4}t_1^{-1}t_2^{-1}t_3^{-1})}.\]
\item The tensor factors involving vector fields and forms contribute a factor of \[-q^{-1/4}(t_1^{-1}+ t_2^{-1} + t_3^{-1}+t_1t_2t_3) + q^{1/4}(t_1+ t_2 + t_3+t_1^{-1}t_2^{-1}t_3^{-1}) - q + q^{-1}.\]
\end{itemize}
\end{proof}

@@

\subsection{States on twisted $AdS_7\times S^{4}$}
\label{s:ads7states}
Next, we consider the sphere reduction of $\mc E^N_{AdS_7}$.
We begin more generally with the case that $X$ is an arbitrary complex three-fold equipped with a square-root of its canonical bundle.
The case of twisted $AdS_7 \times S^4$ corresponds to $X = \C^3$.
As before, we consider the $S^4$ bundle 
\[
\begin{tikzcd}
S^4 \ar[r] & \operatorname{Tot} (\R\oplus K^{1/2}\otimes \C^2\to X) \setminus 0(X) \ar[d, "p"] \\ & \R_{>0}\times X
\end{tikzcd}
\]

@@

\beqn\label{eqn:cotm5}
\Omega^{0,\bullet}_{X} (\mc V_{X}) = T^* _{\alpha} \left (\begin{tikzcd}[row sep = 1 ex] 
\ul{-} & \ul{+} \\
\C[w_1,w_2] \{\partial_{w_a}\} \otimes \Omega^{0,\bullet}_{X} \ar[r, "\del^W_\Omega" description] & \C[w_1,w_2] \otimes \Omega^{0,\bullet}_{X}  \\
\C[w_1,w_2] \otimes \Omega^{0,\bullet}_{X} (\T)\ar[ur, "\del^X_\Omega" description] \\
\C[w_1,w_2] \otimes \Omega^{0,\bullet}_{X} \ar[r, "\del_X" description]\ar[dr, "\del_W" description] & \C[w_1,w_2]\otimes \Omega^{0,\bullet}_{X} (\Omega^1) \\ &  \C[w_1,w_2] \{\d w_a\} \otimes \Omega^{0,\bullet}_{X} 
\end{tikzcd} \right) 
\eeqn
Analogously to the case of $AdS_4\times S^7$, $\alpha$ here denotes the extra $N$-dependent differential induced by bracketing with the flux, which deforms the cotangent bundle.

A natural Lagrangian in the phase space is thus given by $\Omega^{0,\bullet}_{X} (\mc L_{AdS_7})$ where $\mc L_{AdS_7}$ is the complex of vector bundles given by  
\begin{equation}
\begin{tikzcd}[row sep = 1 ex]
    \ul{-} & \ul{+} \\
(w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] & (w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \otimes \mc O \\
(w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \otimes \T\ar[ur, "\del^X_\Omega" description] \\
(w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \otimes \mc{O}\ar[r, "\del_X" description]\ar[dr, "\del_W" description] & (w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}]  \otimes \Omega^1 \\ & (w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \{\d w_a\} \otimes \mc O
\end{tikzcd}
\end{equation}

We now specialize to $X = \C^3$.

\begin{defn}\label{defn:ads7states}
The space of supergravity states on twisted $AdS_7\times S^4$ is given by the costalk at zero of the factorization algebra on $\C^3$ given by 
\beqn
\cO \left(\Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7} ) \right ) .
\eeqn
\end{defn}

@@

\begin{lem}
The space of supergravity states on twisted $AdS_7\times S^4$ is the symmetric algebra $\Sym (\mc H_{AdS_7} )$ where $\mc H_{AdS_7}$ is given by the cochain complex

@@

Indeed, recall that in equations \eqref{eqn:cotm2}, \eqref{eqn:cotm5} we wrote the phase spaces as twisted cotangent bundles, where the nontrivial Poisson tensor was induced by the terms in the differential coming from bracketing with the flux. When we specialize $N=0$, this Poisson tensor vanishes, and there is an additional Lagrangian given by the zero section.

Explicitly these Lagrangians in the phase space are described as follows.
\begin{itemize}
\item Let $\mc L_{AdS_4}^{r=0}$ denote the following complex of vector bundles on $\C$ 
 \begin{equation}
 \begin{tikzcd}[row sep = 1 ex]
   \ul{-} & \ul{+} \\
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] &\C[w_1,\ldots, w_4]  \otimes \mc O \\
\C[w_1,\ldots, w_4]   \otimes \T\ar[ur, "\del^M_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \mc{O}\ar[r, "\del_M" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4]\otimes \Omega^1 \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \mc O
\end{tikzcd}
\end{equation}

The desired Lagrangian in $(p_*\mc E^{0}_{AdS_4})|_{\{\infty\} \times\R\times\C}$ is given by $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc L_{AdS_4}^{r=0})$.

\item Let $\mc L_{AdS_7}^{r=0}$ denote the following complex of vector bundles on $\C^3$
 \begin{equation}
 \begin{tikzcd}[row sep = 1 ex]
   \ul{+} & \ul{-} \\
\C[w_1, w_2] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] &\C[w_1,w_2]  \otimes \mc O \\
\C[w_1, w_2]   \otimes \T\ar[ur, "\del^X_\Omega" description] \\
\C[w_1, w_2] \otimes \mc{O}\ar[r, "\del_X" description]\ar[dr, "\del_W" description] & \C[w_1,w_2]\otimes \Omega^1 \\ & \C[w_1, w_2] \{\d w_a\}  \otimes \mc O
\end{tikzcd}
\end{equation}
The desired Lagrangian in $(p_*\mc E^{0}_{AdS_7})|_{\{\infty\} \times\C^3}$ is given by $\Omega^{0,\bullet}_{X} (\mc L_{AdS_7}^{r=0})$.
\end{itemize}

Note that the same formulae defining the $L_\infty$ structure on the parity shift of the eleven-dimensional theory $\mc E$ \ref{thm:dfn} equip these Lagrangians in the $N=0$ phase spaces with $L_\infty$ structures. Moreover, the canonical maps
\[
\Omega^\bullet_{\R} \otimes \Omega^{0,\bullet}_{\C} (\mc L^{r=0}_{AdS_4} ) \to (p_* \mc E^0 _{AdS_4})|_{\{\infty\} \times \R\times \C}, \quad \Omega^{0,\bullet}_{X} (\mc L^{r=0}_{AdS_7} ) \to (p_* \mc E^0 _{AdS_7})|_{\{\infty\} \times \C^3}
\]
preserve the $L_\infty$ brackets even taking into account the potential for additional higher brackets on the target coming from homotopy transfer. Indeed, such brackets must necessarily involve classes in $H^2_{\mr{THF}} \left ( (\R\times \C^2)\setminus 0 \right )$

@@

The following lemma illustrates that the state space of definitions \ref{defn:ads4states} \ref{defn:ads7states} can also be computed using these alternate boundary conditions.

These Lagrangians afford an alternative description of twisted supergravity states, which will be used to investigate their representation theoretic properties.

\begin{prop}\label{prop:altstates}
There are isomorphisms of cochain complexes
\begin{center}
$\mc U \left ( \Omega^\bullet_\R\otimes \Omega^{0,\bullet}_{\C} (\mc L_{AdS_4}^{r=0} ) \right )(0)\cong \Sym( \mc {H}_{AdS_4} )$ \\
$\mc U \left ( \Omega^{0,\bullet}_{X}(\mc L_{AdS_7}^{r=0})\right )(0)\cong \Sym( \mc {H}_{AdS_7} )$
\end{center}
\end{prop}
\begin{proof}
For a local $L_\infty$ algebra $\mc L$, its factorization envelope $\mc U(L)$ is defined to be $\clie_\bullet (\mc L_c)$ the Lie algebra chains on the cosheaf of compactly supported sections. Therefore, it suffices to show that in each case, the costalk of the cosheaf of comapctly supported sections is quasi-isomorphic to $\mc H_{AdS_4}$ and $\mc H_{AdS_7}$ respectively. This is a consequence of the following observations.

>>>>

%The phase space is equipped with a natural symplectic form given by
%\[
%\int_C \d z \oint_{S^2} \d w \, \alpha \wedge \alpha' .
%\]
%There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bullet}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C - 0$ which extends to zero.
%The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$
\subsection{States on twisted $AdS_4\times S^7$}\label{s:ads4states}
We begin more generally with the input being a three-manifold $M$ equipped with a THF structure of codimension one.
As in \S \ref{s:??} the elliptic complex $\cA^\bu_M$ computes the THF cohomology of $M$.
We denote by $K$ the holomorphic canonical bundle of $M$ which has a local frame given by $\d z$.
The case of $AdS_4 \times S^7$ corresponds to taking $M = \R \times \C$, which we do throughout this section.

We will also fix a fourth-root $K^{1/4}$ of this bundle.
Following the above prescription, we consider the $S^7$ bundle 
\beqn\label{eqn:geomads4}
\begin{tikzcd}
S^7 \ar[r] & \operatorname{Tot} (K^{1/4} \otimes \C^4 \to M) \setminus 0(M) \ar[d, "p"] \\ & \R_{>0}\times M
\end{tikzcd}
\eeqn
We wish to describe the free limit of the pushforward $p_* \mc E^N_{AdS_4}$ as a sheaf of cochain complexes on $\R_{>0}\times M$.

@@

\parsec{}
We proceed to define a natural boundary condition of the twisted $AdS_4$ theory at $\{\infty\} \times M \subset \R_{>0} \times M$. 
Such a boundary condition is specified by a Lagrangian in the phase space whose symplectic structure uses Serre duality on the THF manifold $M$ together with the higher residue pairing along the THF structure of the sphere $S^7$. 
The restriction $(p_* \mc E^N_{AdS_4})|_{\{\infty\}\times \C}$ describes the phase space and is easily seen to be the complex of vector bundles $\cA_M^\bu (\mc V^N)$. 
We wish to describe a shifted Lagrangian therein.

@@

Thus we see that a natural Lagrangian in the phase space is given by the sheaf of cochain complexes $\cA^\bu_M(\mc L^N_{AdS_4})$ where $\mc L^N_{AdS_4}$ is the following complex of holomorphic vector bundles on $M$:

@@

We denote by $\cF_{AdS_4}$ the factorization algebra on $M = \R\times \C$ which assigns to an open set $U \subset \R \times \C$ the cochain complex
\beqn
 \cF_{AdS_4} (U) = \cO\left(\cA^\bu(U,\mc L^N_{AdS_4}) \right ) .
\eeqn
%Here, $\cA^\bu(U, \cL^N_{AdS_4}$

\brian{what's the dependence on $N$?}

\begin{defn}\label{defn:ads4states}
The \emph{space of supergravity states} $\cS_{AdS_4}$ on twisted $AdS_4\times S^7$ is given by the cochain complex given by the costalk at zero of the factorization algebra $\cF_{AdS_4}$:
\beqn
\cS_{AdS_4} \define \cF_{AdS_4} (0) .
\eeqn
\end{defn}

@@

\begin{lem}\label{lem:ads4states}
The space of supergravity states on twisted $AdS_4\times S^7$ is the symmetric algebra 
\beqn
\cS_{AdS_4} = \Sym (\mc H_{AdS_4})
\eeqn
where $\mc H_{AdS_4}$ is the cochain complex
 \begin{equation} 
 \begin{tikzcd}[row sep = 1 ex]
    \ul{-} & \ul{+} \\ 
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \C[\del_z]\delta_{z=0}\ar[r, "\del^W_\Omega" description] & \C[w_1,\ldots, w_4]  \otimes \C[\del_z]\delta_{z=0} \\
\C[w_1,\ldots, w_4] \del_z  \otimes \C[\del_z]\delta_{z=0}\ar[ur, "\del^M_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \C[\del_z]\delta_{z=0}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \d z \otimes \C[\del_z]\delta_{z=0} \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \C[\del_z]\delta_{z=0}
\end{tikzcd}
\end{equation}
\end{lem}

@@

\begin{prop}\label{prop:ads4index}
The single particle index of the space of supergravity states $\mc H_{AdS_4}$ is given by 
\[
f_{AdS_4} (t_1, t_2, t_3, q)  = \frac{q\left (\begin{aligned} q^{1/4}(t_1+ t_2 + t_3+t_1^{-1}t_2^{-1}t_3^{-1}) &+ q^{-1} \\- q^{-1/4}(t_1^{-1}+ t_2^{-1} + t_3^{-1}+t_1t_2t_3) &- q   \end{aligned}\right)}{(1-q)(1-q^{1/4}t_1)(1-q^{1/4}t_2)(1-q^{1/4}t_3)(1-q^{1/4}t_1^{-1}t_2^{-1}t_3^{-1})}
\]
\end{prop}
\begin{proof}
The two summands not involving holomorphic vector fields or forms appear with opposite parity, so their contributions to the character cancel. For the remaining summands, It is straightforward to compute the character of each tensor factor:
\begin{itemize}
\item The factor $\C[\del_z]\delta_{z=0}$ contributes a factor of \[\frac{q}{1-q}.\]
\item The tensor factor $\C[w_1,\cdots, w_4]$ contributes a factor of \[\frac{1}{(1-q^{1/4}t_1)(1-q^{1/4}t_2)(1-q^{1/4}t_3)(1-q^{1/4}t_1^{-1}t_2^{-1}t_3^{-1})}.\]
\item The tensor factors involving vector fields and forms contribute a factor of \[-q^{-1/4}(t_1^{-1}+ t_2^{-1} + t_3^{-1}+t_1t_2t_3) + q^{1/4}(t_1+ t_2 + t_3+t_1^{-1}t_2^{-1}t_3^{-1}) - q + q^{-1}.\]
\end{itemize}
\end{proof}

@@

\subsection{States on twisted $AdS_7\times S^{4}$}
\label{s:ads7states}
Next, we consider the sphere reduction of $\mc E^N_{AdS_7}$.
We begin more generally with the case that $X$ is an arbitrary complex three-fold equipped with a square-root of its canonical bundle.
The case of twisted $AdS_7 \times S^4$ corresponds to $X = \C^3$.
As before, we consider the $S^4$ bundle 
\beqn\label{eqn:geomads7}
\begin{tikzcd}
S^4 \ar[r] & \operatorname{Tot} (\R\oplus K^{1/2}\otimes \C^2\to X) \setminus 0(X) \ar[d, "p"] \\ & \R_{>0}\times X
\end{tikzcd}
\eeqn

@@

\beqn\label{eqn:cotm5}
\Omega^{0,\bullet}_{X} (\mc V_{X}) = T^* _{\alpha_N} \left (\begin{tikzcd}[row sep = 1 ex] 
\ul{-} & \ul{+} \\
\C[w_1,w_2] \{\partial_{w_a}\} \otimes \Omega^{0,\bullet}_{X} \ar[r, "\del^W_\Omega" description] & \C[w_1,w_2] \otimes \Omega^{0,\bullet}_{X}  \\
\C[w_1,w_2] \otimes \Omega^{0,\bullet}_{X} (\T)\ar[ur, "\del^X_\Omega" description] \\
\C[w_1,w_2] \otimes \Omega^{0,\bullet}_{X} \ar[r, "\del_X" description]\ar[dr, "\del_W" description] & \C[w_1,w_2]\otimes \Omega^{0,\bullet}_{X} (\Omega^1) \\ &  \C[w_1,w_2] \{\d w_a\} \otimes \Omega^{0,\bullet}_{X} 
\end{tikzcd} \right) 
\eeqn
Analogously to the case of $AdS_4\times S^7$, $\alpha_N$ here denotes the extra $N$-dependent differential induced by bracketing with the flux, which deforms the cotangent bundle.

A natural Lagrangian in the phase space is thus given by $\Omega^{0,\bullet}_{X} (\mc L_{AdS_7})$ where $\mc L^N_{AdS_7}$ is the complex of vector bundles given by  
\begin{equation}
\begin{tikzcd}[row sep = 1 ex]
    \ul{-} & \ul{+} \\
(w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] & (w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \otimes \mc O \\
(w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \otimes \T\ar[ur, "\del^X_\Omega" description] \\
(w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \otimes \mc{O}\ar[r, "\del_X" description]\ar[dr, "\del_W" description] & (w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}]  \otimes \Omega^1 \\ & (w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \{\d w_a\} \otimes \mc O
\end{tikzcd}
\end{equation}

We denote by $\cF_{AdS_7}$ the factorization algebra on $X = \C^3$ which assigns to an open set $U \subset \C^3$ the cochain complex
\beqn
 \cF_{AdS_7} (U) = \cO\left(\Omega^{0,\bu}(U,\mc L^N_{AdS_7}) \right ) .
\eeqn
\brian{what's the dependence on $N$?}
%Here, $\cA^\bu(U, \cL^N_{AdS_4}$

\begin{defn}\label{defn:ads7states}
The \emph{space of supergravity states} $\cS_{AdS_7}$ on twisted $AdS_7\times S^4$ is given by the cochain complex given by the costalk at zero of the factorization algebra $\cF_{AdS_7}$:
\beqn
\cS_{AdS_7} \define \cF_{AdS_7} (0) .
\eeqn
\end{defn}

@@

\begin{lem}
The space of supergravity states $\cS_{AdS_7}$ on twisted $AdS_7\times S^4$ is the symmetric algebra $\Sym (\mc H_{AdS_7} )$ where $\mc H_{AdS_7}$ is given by the cochain complex

@@

Indeed, recall that in equations \eqref{eqn:cotm2}, \eqref{eqn:cotm5} we wrote the phase spaces as twisted cotangent bundles, where the nontrivial Poisson tensor was induced by the terms in the differential coming from bracketing with the flux. When we specialize $N=0$, this Poisson tensor vanishes, and there is an additional Lagrangian given by the zero section.
Since the back reactions do not appear, these boundary conditions make sense for arbitrary THF three-manifold $M$ in \eqref{eqn:geomads4} and arbitrary threefold $X$ in \eqref{eqn:geomads7}.
We will specialize to $M = \R \times \C$ and $X =\C^3$ again momentarily.

Explicitly these Lagrangians in the phase space are described as follows.
\begin{itemize}
\item Let $\mc L_{AdS_4}^{r=0}$ denote the following complex of vector bundles on $M$
 \begin{equation}
 \begin{tikzcd}[row sep = 1 ex]
   \ul{-} & \ul{+} \\
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] &\C[w_1,\ldots, w_4]  \otimes \mc O \\
\C[w_1,\ldots, w_4]   \otimes \T\ar[ur, "\del^M_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \mc{O}\ar[r, "\del_M" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4]\otimes \Omega^1 \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \mc O
\end{tikzcd}
\end{equation}
The desired Lagrangian in $(p_*\mc E^{0}_{AdS_4})|_{\{\infty\} \times M}$ is given by the complex of bundles $\cA^\bu_{M}(\mc L_{AdS_4}^{r=0})$ on $M$.

\item Let $\mc L_{AdS_7}^{r=0}$ denote the following complex of vector bundles on $X$
 \begin{equation}
 \begin{tikzcd}[row sep = 1 ex]
   \ul{+} & \ul{-} \\
\C[w_1, w_2] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] &\C[w_1,w_2]  \otimes \mc O \\
\C[w_1, w_2]   \otimes \T\ar[ur, "\del^X_\Omega" description] \\
\C[w_1, w_2] \otimes \mc{O}\ar[r, "\del_X" description]\ar[dr, "\del_W" description] & \C[w_1,w_2]\otimes \Omega^1 \\ & \C[w_1, w_2] \{\d w_a\}  \otimes \mc O
\end{tikzcd}
\end{equation}
The desired Lagrangian in $(p_*\mc E^{0}_{AdS_7})|_{\{\infty\} \times X}$ is given by $\Omega^{0,\bullet}_{X} (\mc L_{AdS_7}^{r=0})$.
\end{itemize}

These Lagrangians exist in the fully interacting eleven-dimensional model, which we can encode perturbatively in terms of an $L_\infty$ structure.
In particular, the parity shift of these Lagrangians are equipped with $L_\infty$ structures compatible with the interacting bulk theory in the sense that the morphisms
\begin{align*}
\cA_M^\bu (\mc L^{r=0}_{AdS_4} ) & \to (p_* \mc E^0 _{AdS_4})|_{\{\infty\} \times M}\\
\Omega^{0,\bullet}_{X} (\mc L^{r=0}_{AdS_7} ) & \to (p_* \mc E^0 _{AdS_7})|_{\{\infty\} \times X}
\end{align*}
preserve the $L_\infty$ brackets even taking into account the potential for additional higher brackets on the target coming from homotopy transfer. 
%Indeed, such brackets must necessarily involve classes in $H^2_{\mr{THF}} \left ( (\R\times \C^2)\setminus 0 \right )$

@@

We restrict to the case $M = \R \times \C$ and $X = \C^3$.
The following lemma illustrates that the state space of definitions \ref{defn:ads4states}, \ref{defn:ads7states} can also be computed using these alternate boundary conditions.
These Lagrangians afford an alternative description of twisted supergravity states, which will be used to investigate their representation theoretic properties.

Given any local $L_\infty$ algebra $\cL$ we can consider the factorization algebra $\clie_\bu(\cL_c)$ which assigns to an open set $U$ the cochain complex computing the Lie algebra homology of the $L_\infty$ algebra of compactly supported sections $\clie_\bu (\cL_c(U))$.

\brian{I think gradings need to be fixed.}

\brian{The dependence on $N$ on the RHS is implicit in above definitions. Explain we are setting $N=0$.}

\begin{prop}\label{prop:altstates}
There are isomorphisms of cochain complexes
\begin{align*}
 \left ( \clie_\bu(\cA^\bu_c (\mc L_{AdS_4}^{r=0} )) \right )(0) & \cong \Sym( \mc {H}_{AdS_4} ) \\
\left ( \clie_\bu ( \Omega^{0,\bullet}_{c}(\mc L_{AdS_7}^{r=0})) \right )(0) & \cong \Sym( \mc {H}_{AdS_7} )
\end{align*}
\end{prop}
\begin{proof}
For a local $L_\infty$ algebra $\mc L$, its factorization envelope $\mc U(L)$ is defined to be $\clie_\bullet (\mc L_c)$ the Lie algebra chains on the cosheaf of compactly supported sections. Therefore, it suffices to show that in each case, the costalk of the cosheaf of comapctly supported sections is quasi-isomorphic to $\mc H_{AdS_4}$ and $\mc H_{AdS_7}$ respectively. This is a consequence of the following observations.
